Highly Available Transactions: Virtues and Limitations

### 2013-04-29 writeup/conclusion.tex
More tweaks

\section{Conclusion}
The current state of database software offers uncomfortable and
unnecessary choices between availability and transactional semantics.
Through our analysis and experiments, we have demonstrated how goals
of high availability will remain a critical aspect of many future data
storage systems. Accordingly, we expose a broad design space of Highly
Available Transactions (HATs), which can offer the key benefits of
highly available distributed systems---``always on'' operation during
partitions and low-latency operations---while also providing a family
of transactional isolation levels and replica semantics that have been
adopted in practice.  In taxonomizing this design space, we show that
many transactional guarantees are achievable with high availability,
while a few, like preventing Lost Update and Write Skew, are not. This
offers a useful connection between storage semantics studied in the
database and distributed systems communities. The next challenge is to
return to issues of performance and systems architecture within the
HAT design space.  Based on our understanding of what is desired in
the field and newfound knowledge of what is possible to achieve, we
believe HATs provide a large and useful design space to pursue.

>>>>

\section{Conclusion and Future Work}
The current state of database software offers uncomfortable and
unnecessary choices between availability and transactional semantics.
Through our analysis and experiments, we have demonstrated how goals
of high availability will remain a critical aspect of many future data
storage systems. Accordingly, we expose a broad design space of Highly
Available Transactions (HATs), which can offer the key benefits of
highly available distributed systems---``always on'' operation during
partitions and low-latency operations---while also providing a family
of transactional isolation levels and replica semantics that have been
adopted in practice.  In taxonomizing this design space, we show that
many transactional guarantees are achievable with high availability,
while a few, like preventing Lost Update and Write Skew, are not. This
offers a useful connection between storage semantics studied in the
database and distributed systems communities.

HATs raise several challenges for future study. In this paper, we have
highlighted standardized models, but we would like a more concise
description of which models are and are not achievable in HAT
systems. Similarly, while we have studied the analytical and
experiment behavior of several HAT models, there is substantial work
in further understanding the performance and design of systems within
the large set of HAT models. We also believe it is time to revisit
techniques such as escrow transactions~\cite{escrow},
Sagas~\cite{sagas}, and other long-running transaction support in
order to aid HAT programming. Weakened failure assumptions as in
escrow or in the form of bounded network asynchrony could enable
richer HAT semantics at the cost of general-purpose
availability. Alternatively, there is a range of possible hybrid
systems providing strong semantics during partition-free periods and
weakened semantics during partitions. Based on our understanding of
what is desired in the field and newfound knowledge of what is
possible to achieve, we believe HATs provide a large and useful design
space to explore.

### 2013-04-29 writeup/relatedwork.tex
More tweaks

With HATs, we seek an alternative set of semantics that are still
useful but do not violate requirements for high availability or low
latency. Recent systems proposals such as Swift~\cite{swift},
Eiger~\cite{eiger}, and Bolt-on Causal Consistency~\cite{bolton}
provide transactional causal consistency guarantees with varying
availability and represent a new class of sticky HAT systems.

\pbnote{add TA stuff}

>>>>

With HATs, we seek an alternative set of semantics that are still
useful but do not violate requirements for high availability or low
latency. Recent systems proposals such as Swift~\cite{swift},
Eiger~\cite{eiger}, and Bolt-on Causal Consistency~\cite{bolton}
provide transactional causal consistency guarantees with varying
availability and represent a new class of sticky HAT systems. There
are infinitely many HAT models (i.e., always reading value 1 is
comparable with always returning value 2), but a recent report from UT
Austin shows that no model stronger than causal consistency can be
achieved in a sticky highly available, \textit{one-way convergent}
system~\cite{cac}. This result is promising and complementary to our
results for general-purpose convergent data stores.
